---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# agreement

<!-- badges: start -->
<!-- badges: end -->

The goal of agreement is to ...

## Installation

You can install the released version of agreement from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("agreement")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jmgirard/agreement")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(agreement)
data(fish)
calc_all(fish, categories = c(1, 2, 3), weighting = "identity")
```

## Code of Conduct

Please note that the 'agreement' project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
