---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# agreement

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of the `agreement` package is to calculate estimates of inter-rater reliability using generalized formulas and output results in a tidy dataframe format that makes collecting, bootstrapping, and plotting them easy. The package includes functions for all major chance-adjusted indexes of categorical agreement (i.e., S, gamma, kappa, pi, alpha) as well as all major intraclass correlation coefficients (i.e., one-way and two-way models, agreement and consistency types, and single measure and average measure units).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jmgirard/agreement")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(agreement)
# Load example dataset with 4 raters assigning 12 objects to 5 unordered categories (and missing values)
data(unordered)
print(unordered)
```

```{r}
# Calculate all chance-adjusted indexes of agreement for unordered categories
nominal <- cat_cai(unordered)
summary(nominal, ci = TRUE)
```

```{r}
# Transform results into a tidy data frame
tidy(nominal)
```

```{r}
# Plot the bootstrap resampling distribution with 95% CIs
plot(nominal)
```


```{r}
# Load example dataset with 5 raters assigning 20 objects to 4 ordered categories (and missing values)
data(ordered)
print(ordered)
```

```{r}
# Calculate all chance-adjusted indexes of agreement for ordered categories (with linear weights)
interval <- cat_cai(ordered, weighting = "linear")
summary(interval, ci = TRUE)
```

```{r}
tidy(interval)
```

```{r}
plot(interval)
```

## Code of Conduct

Please note that the 'agreement' project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
